%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Troy A. Brier, PhD}{}
\position{Computational Chemist {\enskip\cdotp\enskip} Biophysicist}
\address{1314 N. DuPont St, Wilmington, DE 19806}

\mobile{(+1) 732-859-9742}
\email{troya.brier@gmail.com}
%\homepage{www.posquit0.com}
%\github{troyb2}
\linkedin{troy-a-brier}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
 \googlescholar{https://scholar.google.com/citations?user=DyTEVjEAAAAJ&hl=en}{T.A. Brier}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}
\newcommand{\companyname}{Synthesize.Bio}
\newcommand{\role}{Bioinformatics Data Engineer}
\newcommand{\brole}{\textbf{\role}}
\newcommand{\erole}{\emph{\role}}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
{\companyname~Recruitment Team}
{\companyname\\1940 5th Avenue West\\Seattle, WA 98119}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for \role}
% How the letter is opened
\letteropening{To whom it may concern,}
%\letteropening{Dear Mr./Ms./Dr. LastName,} %known sender
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
\begin{document}
	
	% Print the header with above personal informations
	% Give optional argument to change alignment(C: center, L: left, R: right)
	\makecvheader[R]
	
	% Print the footer with 3 arguments(<left>, <center>, <right>)
	% Leave any of these blank if they are not needed
	\makecvfooter
	{\today}
	{Troy A. Brier~~~·~~~Cover Letter}
	{}
	
	% Print the title with above letter informations
	\makelettertitle
	
	%-------------------------------------------------------------------------------
	%	LETTER CONTENT
	%-------------------------------------------------------------------------------
	\begin{cvletter}
		\lettersection{About Me}
		%doesnt really need to change job by job as long as they are computational with "research focus"
		I am a physical chemist by training with a background in scientific computing focusing on biological systems.
		Specifically, I have integrated principles from chemistry, physics, and statistics to investigate diverse phenomena within bacterial cells, such as a regulatory mechanisms for stress response and the interplay between the transcriptome and proteome.	
		In my career, I have achieved proficiency in a wide array of computational tools to design and implement analytical pipelines within multiple different environments (HPC, AWS, Docker, Conda) on various operating systems (Linix, MacOS, Windows) leveraging custom and pre-built software packages with standard coding languages (Python, R, Bash, etc).
		Additionally, I have developed skills in designing, managing, and contributing to exploratory multi-year projects that require flexibility, self-assessment, reproducibility, and publication-level documentation.
		I have extensive experience working in highly collaborative environments, domestically and internationally, and I am well practiced in presenting technical material to audiences of varying subject-matter expertise.
				
		\lettersection{Why \companyname?}
		%how do i fit the mission of the company / goals
		My former experience has given me a deep appreciation for scientific innovation and the need for more efficient and accelerated methods to extend innovation beyond the laboratory and into the real world. 	
		Therefore, I am particularly drawn to \companyname's mission to fundamentally change life sciences research and accelerate the pace of biomedical discovery.
		As a start-up in biomedical research, I am inspired by~\companyname's commitment to improve the accessibility of genomic data by reducing the known difficulties with producing and handling such data. 
		Furthermore, \companyname's dedication to empowering scientific exploration with AI/ML tools is appealing to me and aligns with my personal philosophy of wanting to push the boundaries of knowledge using computational innovation.
		I would welcome the opportunity to join your team to contribute to making the company's vision a reality.
		
		\lettersection{Why Me?}
		%should talk about things on the job listing skills i have 
%		I am think I am a quality candidate for the \brole~at the \companyname.
		As a computational chemist and biophysicist I would bring a deep understanding of fundamental biological principles, complemented by hands-on experience in scientific computing across diverse operating systems and environments. %understanding of fundamental biological principles+working proficiency in Unix/Linux operating system
		I have significant knowledge of Python and am proficient in R as tools to solve complex scientific questions including the processing and handling of multiple types of NGS data sets.
		Throughout my career I have worked with many different types and sizes of data sets, so I am confident in my capacity to adapt, manage, and utilize new data sets regardless of size for addressing challenging biological questions.
		 %learn quickly ability to apply skills
		While my AI/ML experience is limited, I very eager to learn more and employ it towards real world applications.
		My ability to achieve and communicate scientific discovery is exemplified through my publication and presentation record.
		In summary, I believe my problem-solving abilities, commitment to learning and integrating novel techniques across disciplines, and aptitude for collaboration makes me an ideal candidate for the \brole~position at~\companyname.
	\end{cvletter}

%	~\newline
%	~\newline
	Thank you for considering my application. I would welcome the opportunity to discuss my qualifications further.
	\newline
%	~\newline
%	~\newline
	%-------------------------------------------------------------------------------
	% Print the signature and enclosures with above letter informations
	\makeletterclosing	
	
\end{document}