%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
% Resume in Latex
% Author : Shubham Mazumder
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
  \hypersetup{
    pdfborder     = 0 0 0,
    pdfpagemode   = UseNone,% do not show thumbnails or bookmarks on opening
    pdfstartpage  = 1,
    pdfcreator    = {\LaTeX{}},
    pdfauthor     = {Troy~A.~Brier},
    pdftitle      = {Troy~A.~Brier -- CV},
    pdfsubject    = {Curriculum Vit\ae{} of Troy~A.~Brier},
    pdfkeywords   = {Troy~A.~Brier, curriculum vit\ae{}, resum\'{e}}
  }
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{amsmath}
\usepackage{soul}
\usepackage{orcidlink}
\usepackage{fontawesome}
%\input{glyphtounicode}
\usepackage[margin=0.5in]{geometry}
%----------FONT OPTIONS----------
% Sans-serif Fonts
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault,light]{inter}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{roboto}
% \usepackage[sfdefault,medium]{InriaSans}
\usepackage[default]{sourcesanspro}
% Serif Fonts
% \usepackage{CormorantGaramond}
% \usepackage{charter}

%-------------------------------------------------------------------------------
%                color scheme definition
%-------------------------------------------------------------------------------
\definecolor{color0}{rgb}{0,0,0}% black
% \definecolor{color1}{rgb}{0.95,0.55,0.15}% orange
%\definecolor{color1}{RGB}{238,66,102}% pink
%\definecolor{color1}{RGB}{14,118,179}% blue
\definecolor{color1}{RGB}{190,15,15}% maroon
% \definecolor{color1}{RGB}{210,69,69}% red
% \definecolor{color1}{RGB}{0,147,143}% teal
\definecolor{color2}{rgb}{0.45,0.45,0.45}% dark grey

% -------------------------------------
%----------PAGE SETUP------------------
% -------------------------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\newcommand{\experienceitemvspace}{3pt}

% Adjust margins
% \addtolength{\oddsidemargin}{0.5pt}
% \addtolength{\evensidemargin}{0.5pt}
% \addtolength{\textwidth}{0.9in}
% \addtolength{\topmargin}{-0.6in}
% \addtolength{\textheight}{1.6in}

% \addtolength{\oddsidemargin}{-.875in}
% \addtolength{\evensidemargin}{-.875in}
% \addtolength{\textwidth}{1.75in}
% \addtolength{\topmargin}{-.875in}
% \addtolength{\textheight}{1.75in}

% URL style
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\Large
}{}{0em}{}[\color{color1}{\titlerule[1.5pt]} \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% ----------- Definitions -----------------------
\def\spaceforrole{ }
\definecolor{lightyellow}{cmyk}{0.00, 0.05, 0.20, 0.00} % Highlights
\sethlcolor{lightyellow} % Highlights

%--------------- Custom commands -----------------------
\newcommand{\sectionspace}{
\vspace{-17pt}
}

\newcommand{\subheadingtitlevspace}{
\vspace{-3pt}
}

% Resume Item
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-4pt}}
  }
}
%%%for insets use
%  \vspace{-2.5pt}
%\begin{itemize}
%\end{itemize}

% Titles
\newcommand{\titleItem}[1]{
  % \textsl{\textbf{#1}}
  \textbf{#1}
}

% Highlighting
\newcommand{\highlight}[1]{
  \textsl{\textbf{#1}}
  % \hl{\textsl{\textbf{#1}}}
  % \textbf{#1}
  % \textsl{\hl{#1}}
}

% Resume Subheading
\newcommand{\resumeSubheading}[4]{
  \item
     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}l@{}l}     
      {#1} & \titleItem{#3} | {#2} & \textit{#4}\\
    \end{tabular*}\vspace{-10pt}
}

% \newcommand{\resumeSubheading}[4]{
%   \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{#3} & \textit{#4} \\
%     \end{tabular*}\vspace{-8pt}
% }

% Resume Sub-sub heading
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{#1} & \textit{#2} \\
    \end{tabular*}\vspace{-2pt}
}

% Resume Project Heading
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & \textit{ #2} \\
    \end{tabular*}\vspace{-9pt}
}

%Resume Subheading List
\newcommand{\resumeSubHeadingListStart}{\subheadingtitlevspace\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

%Resume Item List
\newcommand{\resumeItemListStart}{
% \vspace{-1pt}
\begin{itemize}}
\newcommand{\resumeItemListEnd}{
% \vspace{-6pt}
\end{itemize}\vspace{-8pt}}

%-------------------------------------------------------
%%%%%%%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%
%-------------------------------------------------------
\begin{document}
% --------------------------
%----------HEADING----------
% --------------------------
\begin{flushleft}
    \textbf{\LARGE Troy A. Brier} \\    
    %\textit{Champaign-Urbana, Illinois} {\large $|$}
    \textcolor{color1}{\textit{1314 N. DuPont St. Wilmington, DE 19806}} \\
    \Mobilefone~\textcolor{color1}{\textit{(732)-859-9742}} {\large $|$}
    \href{mailto:troya.brier@gmail.com}{{\Letter~\textcolor{color1}{\textit{troya.brier@gmail.com}}}}
    {\large $|$}
    \href{https://www.linkedin.com/in/troy-a-brier/}{\faLinkedin~\textcolor{color1}{troy-a-brier}}
    {\large $|$}
    \href{https://github.com/troyb2}{\Keyboard~\textcolor{color1}{github.com/troyb2}}
    {\large $|$}
    \href{https://scholar.google.com/citations?user=DyTEVjEAAAAJ&hl=en}{\textcolor{color1}{Google~Scholar~Page}}
    \vspace{-8pt}
\end{flushleft}

% -------------------------------------
%---------- PROFESSIONAL SUMMARY ------
% -------------------------------------
\section{\textcolor{color1}{Professional Summary}}
\vspace{-3pt}
\begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
        {Computational chemist with a background in biological scientific computing.
         Experienced solving diverse problems in computational science settings applying novel techniques across domains.
         Skilled in the design and management of exploratory multi-year projects requiring flexibility, self-assessment mechanisms, and documentation suitable for publication.
         Proficient in presenting technical material to audiences with varying subject-matter expertise.
        } \\
    }}
 \end{itemize}
 \sectionspace
\vspace{3pt}

% -------------------------------------
%----------HEADING---------------------
% -------------------------------------

% \section{Awards and Certifications}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\titleItem{Star Award} \emph{ $|$ Company 1}}{September 2018}
%       \resumeProjectHeading
%           {\titleItem{Kudos Award} \emph{ $|$ Company 2}}{May 2017}
%       \resumeProjectHeading
%           {\titleItem{IBM Full Stack Software Developer} \emph{$|$ IBM}}{November 2023}
%           \resumeProjectHeading
%           {\titleItem{CompTia Sec+} \emph{$|$ CompTia}}{December 2023}
%           \resumeSubHeadingListEnd
          
% -------------------------------------
%----------EDUCATION-------------------
% -------------------------------------
\section{\textcolor{color1}{Education}}
\vspace{-3pt}
{
	\setlength\tabcolsep{0pt}
	\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} llr}
		University of Illinois at Urbana-Champaign~(UIUC) & \textbf{PhD in Chemistry} & \textcolor{color2}{\textit{August 2017 -- December 2024}}\\
		The College of New Jersey~(TCNJ) & \textbf{BS in Chemistry (ACS-certified)} & \textcolor{color2}{\textit{August 2013 -- May 2017}}\\
	\end{tabular*}
}
\sectionspace
\vspace{3pt}

% -------------------------------------
%----------Awards-------------------
% -------------------------------------
\section{\textcolor{color1}{Awards}}
%\vspace{-3pt}
{
	\setlength\tabcolsep{0pt}
	\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} llr}
%		University of Illinois at Urbana-Champaign~(UIUC) & \textbf{PhD in Chemistry} & \textcolor{color2}{\textit{Aug 2017 -- Dec 2024}}\\
%		The College of New Jersey~(TCNJ) & \textbf{BS in Chemistry (ACS-certified)} & \textcolor{color2}{\textit{Aug 2013 -- May 2017}}\\
		Young Scholars Outstanding Mentor Awardee & UIUC & \textcolor{color2}{\textit{Summer 2018}}\\
		Alfred P. Sloan Fellow & UIUC & \textcolor{color2}{\textit{Fall 2017}}\\
		Rodger Adams Fellow & UIUC & \textcolor{color2}{\textit{Fall 2017}}\\
		Hannum Fellow & UIUC & \textcolor{color2}{\textit{Fall 2017}}\\
		Goodkin Physical Chemistry Awardee & TCNJ & \textcolor{color2}{\textit{Spring 2017}}\\
		Research Experience for Undergraduate (REU) & Colorado State University & \textcolor{color2}{\textit{Summer 2016}}\\
		Mentored Undergraduate Summer Experience (MUSE) & TCNJ & \textcolor{color2}{\textit{Summer 2015}}\\
		TCNJ Chairman of the Board Scholar & TCNJ & \textcolor{color2}{\textit{All Semesters}}\\
	\end{tabular*}
}
\sectionspace
\vspace{6pt}

% ----------------------------------
%----------R EXPERIENCE-------------
% ----------------------------------
\section{\textcolor{color1}{Research Experience}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{Graduate/Postdoctoral Research Assistant}} $|$ \emph{Luthey-Schulten Group}, Dept. of Chemistry at UIUC}{\textcolor{color2}{January 2018 -- December 2024}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Doctoral Dissertation: Shaping the bacterial transcriptome: Perspectives from kinetic modeling}
\resumeItem{Constructed a stochastic kinetic model using data collected from super-resolution imaging experiments to simulate the sugar-stress response in \textit{Escherichia coli}.}
\resumeItem{Collaborated in the use of GPU-accelerated, hybrid stochastic-deterministic methods to simulate whole-cell models of bacteria that capture the reaction and diffusion of $\sim$10,000 biochemical components at the cell-scale.}
%  \vspace{-1pt}
  \begin{itemize}
	\setlength\itemsep{-1pt}
	\item Constructed a kinetic model of the nucleotide metabolism for a bacteria cell.
	\item Curated genomics, transcriptomics, proteomics, metabolomics, and kinetic rates data from experiments/databases.
	\item Updated software/code for use on high performance GPU cluster.
\end{itemize}
\vspace{-5pt}
\resumeItem{Developed a methodology to profile the bacterial transcriptome coupling bioinformatics and computational analysis of NGS experiments.
  \vspace{-4pt}
  \begin{itemize}
  \setlength\itemsep{-1.5pt}
  \item Built a sequence alignment based pipeline to identify genetic motifs within a bacterial genome and predict transcriptional events.
  \item Analyzed Illumina, Pacific Biosciences, and Oxford Nanopore Technologies RNA sequencing experiments.
  \item Created tools to predict transcription units and visualize the RNA isoforms.
  \end{itemize}
}\vspace{-2.5pt}
\resumeItem{Assisted PI in preparation of grant materials to acquire federal funding: \emph{NSF~MCB~2221237} - \$2.00M (proposal, annual reports) $|$ \emph{NSF~MCB~1818344} - \$1.50M (annual reports) $|$ \emph{NSF~MCB~1840320} - \$1.18M (annual reports).}
\resumeItem{Maintained group's GPU cluster and website.}
\resumeItem{Collaborated with industrial and academic partners, both domestic and international.}
\resumeItem{Presented research results to broader scientific community at domestic and international conferences.}
\resumeItem{Mentored junior graduate and undergraduate student researchers.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Undergraduate Research Assistant}} $|$ \emph{The Baker Group}, Dept. of Chemistry at TCNJ}{\textcolor{color2}{December 2014 -- May 2017}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Explored individual and multiplte type IV bacterial pilin subunit(s) dynamics and aggregation in a membrane environment using atomistic and MARTINI coarse grained molecular dynamics simulations.}
\resumeItem{Presented research results to broader scientific community at domestic conferences.}
\resumeItem{Mentored junior undergraduate student researchers.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{REU Summer Research Intern}} $|$ \emph{The McCullagh Group}, Dept. of Chemistry at Colorado State University}{\textcolor{color2}{May 2016 -- July 2016}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Worked in the McCullagh Group for a ten-week program consisting of a two week computational chemistry course and a eight week research period.}
\resumeItem{Performed molecular dynamics simulations to develop methodology for ligand binding site identification to aid drug design.}
\resumeItem{Presented poster of results at a poster session.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{MUSE Research Intern}} $|$ \emph{The Baker Group}, Dept. of Chemistry at TCNJ}{\textcolor{color2}{Summer 2015}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Worked in the Baker Biomoleculer Modeling and Simulation group for an eight week program}
\resumeItem{Investigated the effect membrane environments have on type IV pilin subunits from \textit{Neisseria gonorrhoeae} and \textit{Pseudomonas aeruginosa} using atomistic molecular dynamics simulations.}
\resumeItem{Presented research results to broader scientific community at poster session.}
%\resumeItem{Mentored junior undergraduate student researchers.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\sectionspace
%\vspace{9pt}

% ------------------------------------
%----------T. EXPERIENCE--------------
% ------------------------------------
\section{\textcolor{color1}{Teaching Experience}}%include addtional misc exp
\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{STC-QCB Advance Computational Workshop Teaching Assistant}} $|$ NSF STC-QCB at UIUC}{\textcolor{color2}{May 2024}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Served as a mentor to teaching assistants helping to construct and test tutorials to teach about stochastic whole-cell modeling.}
\resumeItem{Installed software used during the workshop to run simulations on supercomputer.}
\resumeItem{Performed minor task as a teaching assistant helping to troubleshoot during the workshop.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Workshop Teaching Assistant}} $|$ NIH Resource for Macromolecular Modeling and Bioinformatics at UIUC}{\textcolor{color2}{October 2021}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Served as a teaching assistant for the online hands-on workshop on computational biophysics hosted by the NIH Resource for Macromolecular Modeling and Bioinformatics.}
\resumeItem{Instructed graduate students and post-doctoral associates from different schools on simulation techniques using the Lattice Microbes stochastic simulation package.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Statistical Thermodynamics Teaching Assistant}} $|$ Dept. of Chemistry at UIUC}{\textcolor{color2}{Fall 2019}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Prepared course materials, graded, and hosted office hours.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Instrumental Analysis Teaching Assistant}} $|$ Dept. of Chemistry at UIUC}{\textcolor{color2}{Fall 2017, Fall 2019}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Supervised laboratory sessions for multiple instruments, prepared course materials, graded, and hosted office hours.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{CPLC Summer School Teaching Assistant}} $|$ NSF CPLC at UIUC}{\textcolor{color2}{July 2019}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Served as a teaching assistant for summer school hosted by the NSF Center for the Physics of Living Cells (CPLC) Summer School---Held lectures for graduate students and post-doctoral associates and prepared tutorials run on AWS instances.}
\resumeItem{ Graduate students and post-doctoral associates from different schools visit the UIUC to learn new 	techniques. With fellow collaborators, instructed the students on how to perform super 	resolution imaging experiments and combine the data with computational techniques.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Math and Science Tutor}} $|$ Tutoring Center at TCNJ}{\textcolor{color2}{Fall 2014 -- Spring 2017}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Tutored fellow students in Calculus I, General Chemistry I, General Chemistry II, Physics 201, Computer Programming I (Java) through the tutoring center. My objective was to provide students with the tools necessary to succeed in their respective courses.}
\resumeItemListEnd

\resumeSubHeadingListEnd
\sectionspace
\vspace{9pt}

% ------------------------------------------
% ----------PUBLICATIONS--------------------
% ------------------------------------------
\section{\textcolor{color1}{Publications {\normalsize (\orcidlinkalt{0000-0002-9530-6517}})}}
% \resumeSubHeadingListStart

\begin{itemize}[leftmargin=0.35in, label={}, labelindent=5pt,itemindent=-15pt]
  \setlength\itemsep{-0.4em}
\item \textcolor{color1}{T. A. Brier}, J. E. Cournoyer, B. R. Gilbert, S. A. Glass, Y. Gao, Z. R. Thornburg, K. Goglin, G. John, T. Mamaghani, S. Shivakumar,   Y. Yu, C. Fields, J. I. Glass, A. P. Mehta, Z. Luthey-Schulten, \textbf{Unraveling the Transcriptional Landscape within a Minimized Bacterium via Comparative Analysis}, \textit{in preparation}

\item T. E. Long, Z. R. Thornburg, B. R. Gilbert, \textcolor{color1}{T. A. Brier}, Z. Luthey-Schulten, J. I. Glass (ed.), \textbf{Chapter --- Determining the Rules of Life of the Minimal Cell Using Whole-Cell Simulation}, \textit{Minimal Genomes and Their Applications,~Royal Society of Chemistry 2024, (in press)}

\item B. R. Gilbert, Z. R. Thornburg, \textcolor{color1}{T. A. Brier}, J. A. Stevens, F. Gr\"{u}newald, J. E. Stone, S. J. Marrink, Z. Luthey-Schulten, \textbf{Dynamics of Chromosome Organization in a Minimal Bacterial Cell}, \href{https://doi.org/10.3389/fcell.2023.1214962}{\textit{Frontiers in Cell and Developmental Biology 2023}}%, \href{https://doi.org/10.3389/fcell.2023.1214962}{DOI:10.3389/fcell.2023.1214962}

\item J. A. Stevens, F. Gr\"{u}newald, P.A. Marco van Tilburg, M. K\"{o}nig, B. R. Gilbert, \textcolor{color1}{T. A. Brier}, Z. R. Thornburg, Z. Luthey-Schulten, S. J. Marrink, \textbf{Molecular Dynamics Simulation of an Entire Cell}, \href{https://doi.org/10.3389/fchem.2023.1106495}{\textit{Frontiers in Chemistry 2023}}%, \href{https://doi.org/10.3389/fchem.2023.1106495}{DOI:10.3389/fchem.2023.1106495}

\item Z. R. Thornburg, D. M. Bianchi, \textcolor{color1}{T. A. Brier}, B. R. Gilbert, T. M. Earnest, M. C.R. Melo, N. Safronova, J. P. S\'{a}enz, A. T. Cook, K. S. Wise, C. A. Hutchison III, H. O. Smith, J. I. Glass, Z. Luthey-Schulten, \textbf{Fundamental Behaviors Emerge from Simulations of a Living Minimal Cell}, \href{https://doi.org/10.1016/j.cell.2021.12.025}{\textit{Cell 2022}}%, \href{https://doi.org/10.1016/j.cell.2021.12.025}{DOI:10.1016/j.cell.2021.12.025}

\item D. M. Bianchi, \textcolor{color1}{T. A. Brier}, A. Poddar, M. S. Azam, C. K. Vanderpool, T. Ha, Z. Luthey-Schulten, \textbf{Stochastic Analysis Demonstrates the Dual Role of Hfq in Chaperoning \textit{E. coli} Sugar Shock}, \href{https://doi.org/10.3389/fmolb.2020.593826}{\textit{Frontiers in Molecular Biosciences 2020}}%, \href{https://doi.org/10.3389/fmolb.2021.644133}{DOI:10.3389/fmolb.2021.644133}

\item Z. R. Thornburg, M. C.R. Melo, D. M. Bianchi, \textcolor{color1}{T. A. Brier}, C. Crotty, M. Breuer, H. O. Smith, C. A. Hutchison III, J. I. Glass, Z. Luthey-Schulten, \textbf{Kinetic Modeling of the Genetic Information Processes in a Minimal Cell}, \href{https://doi.org/10.3389/fmolb.2019.00130}{\textit{Frontiers in Molecular Biosciences 2019}}%, \href{https://doi.org/10.1016/j.cell.2021.12.025}{DOI:10.1016/j.cell.2021.12.025}
\end{itemize}


% ----------------------------------
% ----------Seminars/Talks----------
% ----------------------------------
\section{\textcolor{color1}{Presentations} }
\resumeSubHeadingListStart
	\resumeProjectHeading
	{\titleItem{{Impact of gene expression strategies in near whole-cell models of minimal bacteria}}} {\textcolor{color2}{Biophysical Society Meeting 2024}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, J.E. Cournoyer, B.R. Gilbert, Z.R. Thornburg, J.I. Glass, C.J. Fields, A.P. Mehta, and Z. Luthey-Schulten}
	\resumeItem{\emph{Seminar} presented at the annual Biophysical Society Meeting Feb. 2024 in Philadelphia, PA}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Stochastic simulations of varied gene expression models within minimal bacteria}}} {\textcolor{color2}{JCVI Minimal Workshop 2023}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, B.R. Gilbert, J.I. Glass, and Z. Luthey-Schulten}
	\resumeItem{\emph{Seminar} presented virtually for the JCVI Minimal Workshop 2023, Sept. 2023}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Towards deciphering the influence of genome architecture in minimized bacteria}}} {\textcolor{color2}{Sloan UCEM Conference 2023}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, P. Venepally, J.I. Glass, and Z. Luthey-Schulten}
	\resumeItem{\emph{Seminar} presented at the 8\textsuperscript{th} Annual Sloan UCEM Conference,  Apr. 2023 in Urbana, IL}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Deciphering the influence of genome architecture in minimized bacteria}}} {\textcolor{color2}{Biophysical Society Meeting 2023}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, P. Venepally, J.I. Glass, and Z. Luthey-Schulten}
	\resumeItem{\emph{Poster} presented at the annual Biophysical Society Meeting Feb. 2023 in San Deigo, CA.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Deciphering the influence of genome architecture in JCVI-syn1.0}}} {\textcolor{color2}{JCVI Minimal Workshop 2022}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, J.I. Glass, and Z. Luthey-Schulten}
	\resumeItem{\emph{Seminar} presented virtually for the JCVI Minimal Workshop 2022, Sept. 2022.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Towards deciphering the influence of genome architecture in a minimized bacterial genome}}} {\textcolor{color2}{IPoLs Meeting 2022}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, P. Venepally, J.I. Glass, and Z. Luthey-Schulten}
	\resumeItem{\emph{Seminar} presented at the annual International Physics of Living Systems Meeting Jun. 2022 in Montepellier, France.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Deciphering the influence of genome architecture in a minimized bacterial genome}}} {\textcolor{color2}{American Physical Society Meeting 2022}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, P. Venepally, J.I. Glass, and Z. Luthey-Schulten}
	\resumeItem{\emph{Seminar} presented at the annual American Physical Society Meeting Mar. 2022 in Chicago, IL.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Genome architecture in Syn1.0 and the minimal cell, Syn3A}}} {\textcolor{color2}{JCVI Minimal Cell Workshop 2021}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, P. Venepally, J.I. Glass, and Z. Luthey-Schulten}
	\resumeItem{\emph{Seminar} presented virtually for the JCVI Minimal Cell Workshop 2021 Sept. 2021}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Modeling the nucleotide metabolic network of a genetically minimal cell}}} {\textcolor{color2}{Biophysical Society Meeting 2020}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, D.M. Bianchi, Z.R. Thornburg, M.C.R. Melo, M. Breuer, H.O. Smith, C.A. Hutchison III, K.S. Wise, J.I. Glass, and Z. Luthey-Schulten.}
	\resumeItem{\emph{Poster} presented at the annual Biophysical Society Meeting Feb. 2020 in San Deigo, CA.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Modeling the impact of point mutations on the regulatory potency of the small RNA SgrS}}} {\textcolor{color2}{Biophysical Society Meeting 2019}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, D.M. Bianchi, A. Poddar, M.S. Azam, C.K. Vanderpool, T. Ha, and Z. Luthey-Schulten}
	\resumeItem{\emph{Poster} presented at the annual Biophysical Society Meeting Mar. 2019 in Baltimore, MD.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Developing a method to identify ligand binding sites in proteins using molecular dynamics}}} {\textcolor{color2}{REU Poster Session 2016}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier}, P.T. Lake, and M. McCullagh}
	\resumeItem{\emph{Poster} presented at Colorado State University Research for Undergraduates Experience poster session Aug. 2016 in Fort Collins, CO.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Molecular simulations of type IV pilin subunits from three organisms in a lipid}}} {\textcolor{color2}{American Chemical Society Meeting 2016}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier} and J.L. Baker}
	\resumeItem{\emph{Poster} presented at the American Chemical Society meeting Mar. 2016 in San Diego, CA.}
	\resumeItemListEnd
	
	\vspace{\experienceitemvspace}
	\resumeProjectHeading
	{\titleItem{{Stabilizing effect of a bacterial lipid membrane on type IV pilin subunits}}} {\textcolor{color2}{MUSE Poster Session 2015}}
	\vspace{2pt}
	\resumeItemListStart
	\resumeItem{\textcolor{color1}{T. A. Brier} and J.L. Baker}
	\resumeItem{\emph{Poster} presented at the Mentored Undergraduate Summer Experience poster session hosted at TCNJ Sept. 2015 in Ewing, NJ.}
	\resumeItemListEnd
\resumeSubHeadingListEnd

\sectionspace
\vspace{9pt}
% -------------------------------------
%----------TECHNICAL SKILLS------------
% -------------------------------------
\section{\textcolor{color1}{Technical Skills}}
\subheadingtitlevspace
\begin{itemize}[leftmargin=0.15in, label={}]
	{\item{
			\vspace{1pt}
			% \titleItem{Programming}{: \emph{advanced} --- \textsc{C/C++, fortran, python}, \LaTeX} $|$ \emph{intermediate} --- \textsc{MATLAB} $|$ \emph{basic} --- \textsc{SQL, Bash, CUDA, Emacs Lisp, Tcl}\\
			\titleItem{Programming}{: \textsc{Python, MATLAB, Bash, R, Tcl}, \LaTeX, C/C++, CUDA, HTML}\\
			\vspace{1pt}
			\titleItem{Tools}{: Unix/Linux, MacOS, Windows, AWS, SVN, Git, SSH, Docker, Apptainer, slurm, Jupyter, VScode, MARTINI CG, NVIDIA DGX}\\
			\vspace{1pt}
			\titleItem{Software}{: pandas, matplotlib, seaborn, numpy, scipy, biopython, cobra, HTSeq, pysam, Guppy, minimap2, PyTorch, sklearn, HDF5, VMD, MAFFT, Clustal, BLAST, deepTools, SAMtools, GROMACS, AMBERMD, NAMD, AlphaFold2} \\
			\vspace{1pt}
			\titleItem{Theoretical Training}{:
				\emph{Mathematics} --- Probability Theory, Stochastic Processes, Information Theory, Numerical Analysis, Linear Algebra, ODEs
				$|$ 
				\emph{Science \& Engineering} --- Biophysics, Systems Biology, Bioinformatics, Molecular Dynamics, Equil. and Nonequil. Statistical Physics and Thermodynamics, Quantum Mechanics, Chemical Kinetics}
	}}
\end{itemize}
%\sectionspace

%-----------------------------------------
%----------Additional EXPERIENCE----------
%-----------------------------------------
\section{\textcolor{color1}{Outreach and Activities}}
\resumeSubHeadingListStart
\resumeProjectHeading
{\titleItem{{Luthey-Schulten Group Server Administrator}} $|$ The Luthey-Schulten Group at UIUC}{\textcolor{color2}{Winter 2022 -- Summer 2024}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Maintained research groups DGX and high-performance supercomputer systems.}
\resumeItem{Established usage protocols for the systems, and then taught them to other groups members.}
\resumeItem{Installed containerized (Docker and Apptainer) versions of group software to greatly improve computational performance.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Student Faculty Hiring Committee Member}} $|$ Volunteer Organization at UIUC}{\textcolor{color2}{Fall 2020, Fall 2022 -- Spring 2024}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Represented (physical) chemistry graduate students in the new faculty hiring process.}
\resumeItem{Attended meetings with candidates asking questions related to their teaching and advising strategies.}
\resumeItem{Submitted write ups to the hiring committee about candidates.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Sloan UCEM Mini-Conference}} $|$ Alfred P. Sloan Foundation at UIUC}{\textcolor{color2}{Winter 2018 -- Winter 2023}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Attended a yearly professional development, networking, and research poster session event for Sloan Fellows hosted by the University Center of Exemplary Mentoring at UIUC.}
\resumeItem{Learned about topics such as graduate studies planning, incorporating diversity at the graduate level, successful mentoring methods, and teaching styles.}
\resumeItem{Attended January 2018, 2019, 2020 (virtual), 2021, 2022, 2023.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{SEBA Mentor}} $|$ Student Organization at UIUC}{\textcolor{color2}{October 2022}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Visited a local elementary school to perform scientific demos for the students to teach basic concepts (magnetism, bouncy).}
\resumeItem{Interacted with students to promote positive role models with the St. Elmo Brady Academy (SEBA).}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Google Chicago PhD Summit Participant}} $|$ Google Chicago-Fulton Market, Chicago, IL}{\textcolor{color2}{January 2020}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Accepted to an event highlighting industry opportunities (primarily at Google) for PhD recipients in computer science related fields.}
\resumeItem{Attended a seminar, career panel, and networking event.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Physical Chemistry Student Seminar Selection Committee Member}} $|$ Student Organization at UIUC}{\textcolor{color2}{Fall 2019}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Served on panel of students responsible for choosing guest speakers for the area seminars.}
\resumeItem{Hosted invited speakers, which included research presentations to the visiting faculty during lunch with other fellow committee members.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Poster Judge for ACS Undergrad Conference}}} {\textcolor{color2}{November 2019}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Served as a graduate student poster judge for the ACS Undergraduate conference held at the	University of Illinois at Urbana-Champaign.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Young Scholars Summer Research Program Mentor Facilitator}} $|$ Center for the Physics of Living Cells at UIUC}{\textcolor{color2}{Summer 2019}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Served in a more senior support role for the Young Scholars Summer Research program.}
\resumeItem{Advised two sets of mentor-mentee pairs during the eight week research program, which entailed regular meetings to ensure a productive experience for the high school student.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Institute on Teaching and Mentoring Conference}} $|$ Alfred P. Sloan Foundation at UIUC}{\textcolor{color2}{October 2018}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Attended a multi-day event focused on spreading research, networking, and mentoring/teaching targeted towards under-represented graduate students. }
\resumeItem{Learned strategies for success at the graduate student level as well as at the faculty level.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Young Scholars Summer Research Program Mentor}} $|$ NSF Center for the Physics of Living Cells at UIUC}{\textcolor{color2}{Summer 2018}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Mentored a local area high school student for an eight-week research program tailored to teach about research and the skills necessary to be a productive scientist.} 
\resumeItem{Advised the student on a metabolic kinetic modeling project, which culminated in a poster presentation at the end of the research program.}
\resumeItem{Recognized as an \emph{outstanding mentor} by the program.}
\resumeItemListEnd

\vspace{\experienceitemvspace}
\resumeProjectHeading
{\titleItem{{Encouraging Tomorrow Chemist Mentor}} $|$ Student Organization at UIUC}{\textcolor{color2}{Spring 2018}}
\vspace{2pt}
\resumeItemListStart
\resumeItem{Performed scientific demos for local middle school students focusing on promoting science to youth and teaching them about basic concepts such as luminescence.}
\resumeItemListEnd

\resumeSubHeadingListEnd
%\sectionspace
%\vspace{9pt}
\end{document}