%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Troy A. Brier, PhD}{}
\position{Computational Chemist {\enskip\cdotp\enskip} Biophysicist}
\address{1314 N. DuPont St, Wilmington, DE 19806}

\mobile{(+1) 732-859-9742}
\email{troya.brier@gmail.com}
%\homepage{www.posquit0.com}
%\github{troyb2}
\linkedin{troy-a-brier}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
 \googlescholar{https://scholar.google.com/citations?user=DyTEVjEAAAAJ&hl=en}{T.A. Brier}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}
\newcommand{\companyname}{Wistar Institute}
\newcommand{\role}{Bioinformatics Analyst}
\newcommand{\brole}{\textbf{\role}}
\newcommand{\erole}{\emph{\role}}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
{Wistar Institute Recruitment Team}
{The \companyname\\3601 Spruce Street\\Philadelphia, PA 19104}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for \role}
% How the letter is opened
\letteropening{To whom it may concern,}
%\letteropening{Dear Mr./Ms./Dr. LastName,} %known sender
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Curriculum Vitae}

%-------------------------------------------------------------------------------
\begin{document}
	
	% Print the header with above personal informations
	% Give optional argument to change alignment(C: center, L: left, R: right)
	\makecvheader[R]
	
	% Print the footer with 3 arguments(<left>, <center>, <right>)
	% Leave any of these blank if they are not needed
	\makecvfooter
	{\today}
	{Troy A. Brier~~~·~~~Cover Letter}
	{}
	
	% Print the title with above letter informations
	\makelettertitle
	
	%-------------------------------------------------------------------------------
	%	LETTER CONTENT
	%-------------------------------------------------------------------------------
	\begin{cvletter}
		\lettersection{About Me}
		%doesnt really need to change job by job as long as they are computational with "research focus"
		I am a physical chemist by training with a background in scientific computing focusing on biological systems.
		Specifically, I have integrated principles from chemistry, physics, and statistics to investigate diverse phenomena within bacterial cells, such as a regulatory mechanisms for stress response and the interplay between the transcriptome and proteome.	
		In my career, I have achieved proficiency in a wide array of computational tools to design and implement analytical pipelines within multiple different environments (HPC, AWS, Docker, Conda) on various operating systems (Linix, MacOS, Windows) leveraging custom and pre-built software packages with standard coding languages (Python, R, Bash, etc).
		Additionally, I have developed skills in designing, managing, and contributing to exploratory multi-year projects that require flexibility, self-assessment, reproducibility, and publication-level documentation.
		I have extensive experience working in highly collaborative environments, domestically and internationally, and I am well practiced in presenting technical material to audiences of varying subject-matter expertise.
				
		\lettersection{Why the \companyname?}
		%how do i fit the mission of the company / goals
		My former experience has given me a deep appreciation for scientific innovation and more importantly the obligation to extend  innovation beyond the laboratory and into the real world. 	
		Therefore, I am particularly drawn to the \companyname's mission to accelerate research advances from bench to bedside in biomedical areas that are critical to society.
		Furthermore, the \companyname's dedication to collaborative science is important to me and aligns with my preferred working environment. 
		As a leader in biomedical research, I am inspired by the~\companyname's commitment (and track record) of producing novel and courageous scientific discoveries.  
		I would welcome the opportunity to join your team to contribute to making the institute's vision a reality.
		
		\lettersection{Why Me?}
		%should talk about things on the job listing skills i have 
%		I am think I am a quality candidate for the \brole~at the \companyname.
		As a computational chemist and biophysicist I would bring a deep understanding of fundamental biological principles, complemented by hands-on experience in scientific computing across diverse operating systems and environments. %understanding of fundamental biological principles+working proficiency in Unix/Linux operating system
		I have significant knowledge of Python and am proficient in R as tools to solve complex scientific questions. %knowledge of R, and/or Python scripting language + basic proficiency in statistical testing
		My ability to achieve and communicate scientific discovery is exemplified through my publication and presentation record. %strong problem solving and communication skills required
		While I am not directly experienced with the mentioned repositories, I have proven my capacity to adapt and utilize new data sets to address challenging biological questions.%familiarity with repositories of genomic data sets and analysis tools, such as TCGA, ICGC, COSMIC, ENCODE, ExAc, UCSC Genome Browser
		~In summary, I believe my problem-solving abilities, commitment to learning and integrating novel techniques across disciplines, and aptitude for collaboration makes me an ideal candidate for the \brole~ position at the \companyname.
	\end{cvletter}

%	~\newline
%	~\newline
	Thank you for considering my application. I would welcome the opportunity to discuss my qualifications further.
	\newline
	~\newline
%	~\newline
	%-------------------------------------------------------------------------------
	% Print the signature and enclosures with above letter informations
	\makeletterclosing	
\end{document}