%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}
% \definecolor{awesome}{RGB}{190,15,15}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Troy A. Brier, PhD}{}
\position{Computational Chemist {\enskip\cdotp\enskip} Biophysicist}
\address{1314 N. DuPont St, Wilmington, DE 19806}

\mobile{(+1) 732-859-9742}
\email{troya.brier@gmail.com}
%\homepage{www.posquit0.com}
%\github{troyb2}
\linkedin{troy-a-brier}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
 \googlescholar{https://scholar.google.com/citations?user=DyTEVjEAAAAJ&hl=en}{T.A. Brier}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}
\newcommand{\companyname}{Quest Dianostics}
\newcommand{\role}{Senior Bioinformatics Engineer}
\newcommand{\brole}{\textbf{\role}}
\newcommand{\erole}{\emph{\role}}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
{\companyname~Recruitment Team}
{\companyname\\
500 Plaza Drive\\
Secaucus NJ, 07094}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for \role}
% How the letter is opened
\letteropening{To whom it may concern,}
%\letteropening{Dear Mr./Ms./Dr. LastName,} %known sender
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{CV}
%-------------------------------------------------------------------------------
\begin{document}
	% Print the header with above personal informations
	% Give optional argument to change alignment(C: center, L: left, R: right)
	\makecvheader[R]
	% Print the footer with 3 arguments(<left>, <center>, <right>)
	% Leave any of these blank if they are not needed
	\makecvfooter
	{\today}
	{Troy A. Brier~~~·~~~Cover Letter}
	{}
%	{CV~~Attached}
%	{Resum\'{e}~~Attached}
	% Print the title with above letter informations
	\makelettertitle
	%-------------------------------------------------------------------------------
	%	LETTER CONTENT
	%-------------------------------------------------------------------------------
	\begin{cvletter}
%		\vspace{-15pt}
%		\lettersection{About Me}
%		\vspace{-7.5pt}
%		doesnt really need to change job by job as long as they are computational with "research focus"

		I am a physical chemist by training with a background in scientific computing, specializing on biological systems.
		Specifically, I have integrated principles from chemistry, physics, and statistics to investigate diverse phenomena within bacterial life, such as regulatory mechanisms for stress response and the interplay between the transcriptome and proteome.	
		In my career, I have achieved proficiency in a wide array of computational tools to design and implement analytical pipelines within multiple computing environments (HPC, AWS, Docker, Conda) on various operating systems (Linux, MacOS, Windows) leveraging both custom and pre-built software with standard coding languages (Python, R, Bash, etc).
		Additionally, I have developed skills in designing, managing, and contributing to exploratory multi-year projects that require flexibility, self-assessment, reproducibility, and publication-level documentation.
		I have extensive experience working in highly collaborative environments, both domestically and internationally, and I am well practiced in presenting technical material to audiences of varying subject-matter expertise. On a personal note, I view science as a tool I can use to make a real difference in the world. I am driven by this and strive to find a company in which I can make that a reality. %I would describe myself as a motivated, adaptable, team player, who looks to contribute however I can. I appreciate the Alaka`ina Foundation's commitment to serve their clients to provide solutions for their communities, One Team with One Mission.
		
		
%		\vspace{-10pt}
%		\lettersection{Why \companyname?}
%		\vspace{-7.5pt}
%		how do i fit the mission of the company / goals
		My former experience has given me a deep appreciation for scientific innovation and the need for more efficient and accelerated methods to translate innovation from the laboratory into real-world impact.
		%Therefore, 
		I am motivated by the \companyname's mission to restore Earth to a healthier state with bioscience and genetics.
		I am particularly drawn to~\companyname's desire to restore extinct species. Having previously contributed to fundamental science, I appreciate the quest for knowledge, but even more so the challenging opportunity it brings, which will lead to the development of new methods and tools for the future.
%		I appreciate that this also extends to the partners for the company, pharma companies and research institutes, emphasizing to me an investment in improving therapeutics in the present but also in the future.
%		Furthermore, \companyname's dedication to empowering scientific exploration with AI/ML tools is appealing to me and aligns with my personal philosophy of wanting to push the boundaries of knowledge using computational innovation.
%		I appreciate the stress on the emphasis on deciphering complex relationships within data, and the insights that can emerge from such analysis.
		I am excited at the opportunity to join the \companyname~team and contribute to its vision with my computational skills.
		
%		\vspace{-10pt}	
%		\lettersection{Why Me?}
%		\vspace{-7.5pt}
		%should talk about things on the job listing skills i have 
%		I am think I am a quality candidate for the \brole~at the \companyname.
		As a computational chemist and biophysicist, I would bring a deep understanding of biological research complemented by hands-on multi-year experience in scientific computing across diverse computing%systems and 
		~environments. %understanding of fundamental biological principles+working proficiency in Unix/Linux operating system
%		Specifically, I have worked closely with synthetic biologist and understand the highly complex nature of engineering biological phenomena.
		I have significant experience with Python and BASH, and am proficient in R as tools to solve complex scientific questions such as developing custom code for simulation and data analysis.
		Throughout my career I have worked with many data sets of varying types and sizes, and am confident in my capacity to adapt, manage, and utilize new data sets to address challenging questions, regardless of data complexity. 
		My experience in the construction of whole-cell models highlights my ability to synergize multi-omics data for biological phenotype prediction. 
		Also, relevant to the position is my previous experience with NGS sequencing data from varying methodologies (Illumina, PacBio, and ONT), where I integrated various bioinformatics software and algorithms to compare and predict complex relationships between the transcriptome and proteome. 
%		This included comparing proteomic data to the results to better understand transcriptome-proteome relationships. 
%		Most relevant to the position is my previous experience with NGS sequencing data from varying methodologies (Illumina, PacBio, and ONT), where I integrated various software and algorithms to compare and predict complex relationships between the data sets. 
%		This included comparing proteomic data to the results to better understand transcriptome-proteome relationships. 
		 %learn quickly ability to apply skills
		My AI/ML experience is currently foundational. I have applied pre-built AI/ML approaches such as AlphaFold2 to aid in discovery. While I have no appreciable experience in constructing AI/ML solutions, I am eager to learn more about how their development.% to synergize AI/ML to enhance scientific discovery.
		%employ them towards real world applications. 		
%		I am confident I can work with diverse groups having collaborated with scientists from different technical and cultural backgrounds.
%		My ability to achieve and communicate scientific discovery is exemplified through my publication and presentation record.
%		I was impressed by the personal traits section of the job posting. I think it is crucial to remember we, as scientist, are people with vastly different personalities. A successful team is composed of diverse people who work together as a cohesive unit. I resonate strongly with the concept of prioritizing "We" over "I". In my opinion, such a mindset is necessary to make a real impact, something I aspire to accomplish. I describe myself as someone with a growth mindset. I believe someone should always being striving for progress. Consistent small improvement can lead to significant change. 
		~In summary, I believe my problem-solving abilities, commitment to learning and integrating novel techniques across disciplines, and aptitude for collaboration make me an ideal candidate for the \brole~position at~\companyname.
%		~\newline
%
		Thank you for considering my application. I would welcome the opportunity to discuss my qualifications further.
	\end{cvletter}

%	\newline
	%-------------------------------------------------------------------------------
	% Print the signature and enclosures with above letter informations	
	\makeletterclosing
\end{document}