%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-orange}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{profile}
\name{Troy A. Brier, PhD}{}
\position{Computational Chemist {\enskip\cdotp\enskip} Biophysicist}
\address{1314 N. DuPont St, Wilmington, DE 19806}

\mobile{(+1) 732-859-9742}
\email{troya.brier@gmail.com}
%\homepage{www.posquit0.com}
%\github{troyb2}
\linkedin{troy-a-brier}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
 \googlescholar{https://scholar.google.com/citations?user=DyTEVjEAAAAJ&hl=en}{T.A. Brier}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%\quote{``Be the change that you want to see in the world."}
\newcommand{\companyname}{Natera}
\newcommand{\role}{Bioinformatics Engineer}
\newcommand{\brole}{\textbf{\role}}
\newcommand{\erole}{\emph{\role}}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
{\companyname~Recruitment Team}
{\companyname\\
201 Industrial Rd\\
San Carlos, CA 94070}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for \role}
% How the letter is opened
\letteropening{To whom it may concern,}
%\letteropening{Dear Mr./Ms./Dr. LastName,} %known sender
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
%\letterenclosure[Attached]{Resume}

%-------------------------------------------------------------------------------
\begin{document}
	
	% Print the header with above personal informations
	% Give optional argument to change alignment(C: center, L: left, R: right)
	\makecvheader[R]
	
	% Print the footer with 3 arguments(<left>, <center>, <right>)
	% Leave any of these blank if they are not needed
	
	\makecvfooter
	{\today}
	{Troy A. Brier~~~·~~~Cover Letter}
	{}
	
	% Print the title with above letter informations
	\makelettertitle
	\vspace{-10pt}
	%-------------------------------------------------------------------------------
	%	LETTER CONTENT
	%-------------------------------------------------------------------------------
	\begin{cvletter}
		\lettersection{About Me}
		%doesnt really need to change job by job as long as they are computational with "research focus"
		I am a physical chemist by training with a background in scientific computing, specializing on biological systems.
		Specifically, I have integrated principles from chemistry, physics, and statistics to investigate diverse phenomena within bacterial life, such as regulatory mechanisms for stress response and the interplay between the transcriptome and proteome.	
		In my career, I have achieved proficiency in a wide array of computational tools to design and implement analytical pipelines within multiple computing environments (HPC, AWS, Docker, Conda) on various operating systems (Linux, MacOS, Windows) leveraging both custom and pre-built software with standard coding languages (Python, R, Bash, etc).
		Additionally, I have developed skills in designing, managing, and contributing to exploratory multi-year projects that require flexibility, self-assessment, reproducibility, and publication-level documentation.
		I have extensive experience working in highly collaborative environments, both domestically and internationally, and I am well practiced in presenting technical material to audiences of varying subject-matter expertise.
		
				
		\lettersection{Why \companyname?}
		%how do i fit the mission of the company / goals
		My former experience has given me a deep appreciation for scientific innovation and the need for more efficient and accelerated methods to extend innovation beyond the laboratory and into the real world. 	
		Therefore, I am particularly drawn to \companyname's mission to make personalized genetic testing and diagnostics part of the standard of care to protect health and enable earlier and more targeted interventions that lead to longer, healthier lives.
		Human biology is complex, and the treatment for one is not guaranteed to be the treatment for another.
		I am inspired by~\companyname's commitment as a global leader in medical testing working to fundamentally change the management of disease worldwide by implementing relatively simple testing to detect disease early and proactively inform treatment.		
%		Furthermore, \companyname's dedication to empowering scientific exploration with AI/ML tools is appealing to me and aligns with my personal philosophy of wanting to push the boundaries of knowledge using computational innovation.
		I am excited at the opportunity to join the \companyname~team and contribute to its vision with my computational skills.
				
		
		\lettersection{Why Me?}
		%should talk about things on the job listing skills i have 
%		I am think I am a quality candidate for the \brole~at the \companyname.
		As a computational chemist and biophysicist I would bring a deep understanding of biological research complemented by hands-on experience in scientific computing across diverse operating systems and environments. %understanding of fundamental biological principles+working proficiency in Unix/Linux operating system
		I have significant knowledge of Python and am proficient in R as tools to solve complex scientific questions including developing custom code for simulation and data analysis.
		TThroughout my career I have worked with many data sets of varying type and size, and I am confident in my capacity to adapt, manage, and utilize new data sets  to address challenging questions, regardless of data size.
		Most relevant to the position is my previous experience with NGS sequencing data from varying methodologies (Illumina, PacBio, and ONT), where I integrated various software and algorithms to compare and predict complex relationships between the data sets. 
		 %learn quickly ability to apply skills
%		While my AI/ML experience is currently foundational, I have experience with AI/ML approaches such as AlphaFold2 and ChatGPT, and I am  very eager to learn more and employ them towards real world applications.
%		My ability to achieve and communicate scientific discovery is exemplified through my publication and presentation record.
		In summary, I believe my problem-solving abilities, commitment to learning and integrating novel techniques across disciplines, and aptitude for collaboration makes me an ideal candidate for the \brole~position at~\companyname.
		
	\end{cvletter}
%	~\newline
%	~\newline

	Thank you for considering my application. I would welcome the opportunity to discuss my qualifications further.
%	\newline
%	\newline
%	~\newline
	%-------------------------------------------------------------------------------
	% Print the signature and enclosures with above letter informations	
	
	\makeletterclosing
\end{document}